Note about WSC

### 2015-03-18 notes.tex
alpha's data for each mu values

\documentclass[a4paper]{article}
\usepackage{fontspec}
\usepackage{amsmath}
\usepackage{amssymb}

@@

\subsection{Verification}
First we verify that our model implements well the already known cultural evolution mechanisms.

@@

@@

In that case individual owns a vector of $n$ traits. One a cultural exchange occurs the whole vector is exchanged.

Individual carries multiples traits (ie price in our experiment), we check that it does not change the result of the algorithm in the long terms, each traits will evolve following the same curves than when just one trait is evolving. The results are shown in figures \ref{fig:10resources}. Those results are statistically the same than those from the previous experiments.
\begin{figure}[h]
	\begin{center}
		\includegraphics[width=6cm]{img/10resources.png}
	\end{center}
	\caption{$\mu=\{.08,.098\}$ for 10 resources}
	\label{fig:10resources}
\end{figure}

\section{Cultural Mechanisms Comparison}

Now that we have shown our model reproduce well known cultural evolution mechansims we will compare the evolution of the system when it is submit to the previous mechanism studied to the evolution of the same system submitted to the mechanisms cultural transmission and innovation used by \cite{gintis2006theemergenceofapricesystemfromdecentralizedbilateralexchange}.

\subsection{framework Adjustment}
In order to allow such comparison we will do our simulation using the same parameters used by Gintis which are : a population with 100 agents per good assuming six good so 600 agents evolving during 1500 steps and with a innovation rate of .01.

@@

@@

\begin{figure}[hbp]
	\begin{center}
		\includegraphics[width=6cm]{img/powerABCD.png}
	\end{center}
	\caption{power law for each exp define in table \ref{tab:exp} after 2000 step}
	\label{fig:powerABCD}
\end{figure}

>>>>

\documentclass[a4paper]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}

@@

\subsection{Statistical Analysis}
In order to test if the data fit power law curve aand to know the parameters off such learning curve, we will used to R Cran Package poweRlaw \cite{gillespie2015fittingheavytaileddistributionsthepowerlawpackage} wich is based on \cite{clauset2009powerlawdistributionsinempiricaldat}. This package allow us to fit the datas with a power law and to know the parameters of this fitted power law ($\alpha$). Moreover, it allows use to test if the datas are actually following the fitted power law using a bootstrapping method that calcul kolmogorv smirnov coefficient.

\subsection{Verification}

First we verify that our model implements well the already known cultural evolution mechanisms.

@@

And as them we find the same between $\alpha$ and $\mu$ (cf tab :\ref{tab:mualpha} \& tab \ref{tab:Bmualpha}).
\begin{figure}[hbp]
	\begin{center}
		\includegraphics[width=7cm]{img/alphawrtmu.png}
	\end{center}
	\caption{$\alpha$  wrt. $\mu$ }
	\label{fig:alphamu}
\end{figure}

\begin{table}
	\centering
	\begin{tabular}{l|cc}
			$\mu$ & $\alpha$ & SD\\\hline
			0.008&1.539122&0.010154623\\
			0.018&1.550888&0.005487468\\
			0.028&1.564014&0.004155942\\
			0.038&1.572597&0.003297191\\
			0.048&1.586550&0.003965373\\
			0.058&1.593909&0.002497322\\
			0.068&1.608492&0.003090030\\
			0.078&1.617235&0.002188951\\
			0.088&1.627801&0.003247013\\
			0.098&1.637116&0.002900783\\
	\end{tabular}
	\caption{Mean \& SD are done with 10 run for each $\mu$}
	\label{tab:mualpha}
\end{table}

\begin{table}
	\centering
	\begin{tabular}{l|cc}
$\mu$&$\alpha$&(SD)\\\hline
0.004&1.50&(0.02) \\
0.008&1.52&(0.02)\\
0.016&1.55&(0.03)\\
0.032&1.59&(0.06)\\
0.064&1.78&(0.08)\\
0.128&1.99&(0.04)\\
	\end{tabular}
	\caption{Mean \& SD from \cite{bentley2004randomdriftandculturechange} }
	\label{tab:Bmualpha}
\end{table}

@@

In that case individual owns a vector of $n$ traits (price in our experiment). When a cultural exchange occurs the whole vector is exchanged and each traits  had a $\mu$ probability to mutate.

Here we check that it does not change the result of the algorithm in the long terms and that each traits will evolve following the same curves than when just one trait is evolving. The results are shown in figures \ref{fig:10resources}. Those results are statistically the same than those from the previous experiments.

\begin{figure}[h]
	\begin{center}
		\includegraphics[width=6cm]{img/10resources.png}
	\end{center}
	\caption{$\mu=\{.08,.098\}$ for 10 resources}
	\label{fig:10resources}
\end{figure}

\section{Cultural Mechanisms Comparison with economical evolution}

Now that we have shown that our model reproduce well the well known cultural evolution mechanisms, and that even when multiple price are simultaneously evolved, we will compare the evolution of the system when it is submit to different mechanisms of transmission and innovation. The one we will use and compare with those used previously are those used by \cite{gintis2006theemergenceofapricesystemfromdecentralizedbilateralexchange}.

\subsection{Framework Adjustment}
In order to allow such comparison we will do our simulation using the same parameters used by Gintis which are : a population with 100 agents per good assuming six good so 600 agents evolving during 1500 steps and with a innovation rate of .01.

@@

\subsection{Gintis' imitation mechanism}
The imitation mechanism is ``score biased'', meaning that people tends to copy the price vector of other that exhibits a high score. This score is computed using the utility function and is summed for every 10 step during a evaluation periode. After those 10 step of evaluation the exchange is done between agents

In its new paper agents adapt themselves using learning simple rules that could be useful to have quicker improvement (and a more cognitively accurate model):

\begin{quotation}
	After each trading period, agents consume their consumption inventories provided they have a positive amount of each consumption good, and agents replenish their inventories of their production goods. Moreover, each trader updates his private price vector on the basis of his trading experience over the period, raising the price of a consumption or production good by 0.02\% if his inventory is empty (i.e.,if he failed to purchase any of the consumption good or sell all of his production good), and lowering price by 0.02\% otherwise (i.e., if he succeeded in obtaining his consumption good or sold all his production inventory).In general, it would be desirable to allow this adjustment strategy to evolve endogenously according to learning or imitation processes, but I have not investigated this possibility.
	\\\cite[p. 7]{gintis2010thedynamicsofgeneralizedmarketexchange}
\end{quotation}

\subsubsection{The utility function \& Barter Process}
The utility function is computed depending on the quantity that agent had collected during the trade. Those quantities are themselves defined by the Barter Process in order to maximise this utility function and depend on the private price of both trader.

\subsection{Gintis' innovation mechanism}

@@

\begin{figure}[hbp]
	\begin{center}
%		\includegraphics[width=6cm]{img/powerABCD.png}
	\end{center}
	\caption{power law for each exp define in table \ref{tab:exp} after 2000 step}
	\label{fig:powerABCD}
\end{figure}
